Review of Group 8 by Group 1

### 2015-02-13 rmtw/a3/latex8.tex
First draft of introduction. Added bib file also

​\Section{Introduction}
*5 references must be used to support claims in Introduction
Use parts of Abstract and Intro from CM.

Coping with change in the software development domain is difficult at best, this is further exasperated by trying to apply changes that do not mesh well with existing development paradigms. How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?

@@

Little existing literature.
There are gaps: see: nothing about applying changes to two different paradigms at the same time.

\SubSection{Deficiencies in Literature}
What is missing

\SubSection{Motivation for Research}
Academia: Has not been done before. (I.e. all CM papers talk about implementing something in a homogenous environment). 
Industry: It's useful to Ericsson. They have had problems implementing changes and keeping up with the competition. It might be good to look up other companies which use MDSD and make a case for them as well.

>>>>

​\Section{Introduction}

Coping with change in the software development domain is difficult at best, it is further exasperated by trying to apply changes that do not mesh well with existing development paradigms. How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?

@@

According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI) or change management (CM) strategies [CITE BOTH].

SPI is X and is usually performed with XYZ

Similar to SPI is the concept of Evidence Based Software Engineering \cite{dyba2005evidence}. EBSE can be used as support for SPI, as suggested by the creators of the strategy. The main aim of which is to find a technology which is suitable for use and to then implement it in an organisation.

Literature tells us that there are many factors for both success and failure when implementing change. X define this type of activity as Software Process Improvement (SPI) [GET REF]. SPI utilises many methods and techniques to implement changes in a companies existing software process.

CMMI is such an example of one of these methods.

In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK. The study focused mostly on how the companies perform SPI and how effective their efforts were. The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.

A further, more specific example is a study conducted by Staron \cite{staron2006adopting}. In this study a case study is conducted with two companies wishing or in the process of adopting MDSD. In the findings, Staron provides a set of conditions for adopting MDSD, one being the compatibility of MDSD and existing principles in the company. Staron states that the adoption of this new process must be usable by the previous processes in place \cite{staron2006adopting}. He concludes by stating that this compatibility is especially important for larger companies due to the heavy effort required to implement the change. In a second study \cite{staron2008transitioning}, Staron provides possible reasons for the adoption of MDSD to fail. He suggests that the large investment in time and money, immature technology and organisational resistance are all factors to overcome in the adoption of new processes.

However, there are is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.

\SubSection{Motivation for Research}
Performing this study would therefore be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone to further research.

Industry are just as likely to be interested. We have performed this study at an organisation, to which the results would be of great value. The organisation in question has had problems in the past with implementing effective change to keep up with their competition.

Furthermore, companies that operate in a similar, or even a different manner would most likely be able to appreciate the efforts made in the study. In the most hopeful of cases, applying the lessons learned to their own situations.

Given that MDSD has seen a considerable rise in adoption by many companies\cite{millermda}, the results of the research would undoubtedly be of use to these companies also.
